Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-16 paper/ms.tex
few changes in paper

where the sum is done over all the $13$ angle values $\theta_i$ where the
ACF has been computed. In Figure XX we plot this statistic for all the
models considered. In all cases $\chi^{2}<7$ which is not sufficient
to consider that the correlation functions from the simulations are
statistically different from the observational one. The constribution
of cosmic variance in the simulations together with the statistical
uncertainties make all tested models compatible with the observational
constraints.

@@

The fitting is done to both the mean ACF and the observational
ACF reported by \cite{Hayashino2004} .  The results are shown 
in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
plane where the average and standard deviation for each mock 
are shown in comparison with the result derived from observations. 
Error bars in these figures represents the standard deviation of the
ACF over all the sub-fields.

It can be seen in the left panel figure \ref{figure:correlation_parameters} that
The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
constrains on the parameters models. Only models with angular-correlation lenght within  
$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.

@@

In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF.

Finally, we also present the ACF in the case of the full SSA22
region which has been homogeneously observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions.

In Figure X we present the results for the models. The full list of
these correlation functions can be found in the the data repository
for this paper in \verb"github".

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\end{center}
\caption{Best models when both the constraints on the maximal number
  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
  0.2$ are included. \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*} 
%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
%\end{center} 
%\caption{ mean ACFs   and their correponding standard deviation (error
%  bars)  of some selected models in different mass ranges over the 7
%  subfields of the SSA22 field (left) and the entire 12 field sample
%  (rigth) using the  random
%  configuration. \label{figure:correlation_random} }   
%\end{figure*}

@@

When we include the tightest constraints on the mock catalogs, we find
that there are 30 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$: the distribution of the number density,
the inferred values for the average occupation fraction. The
consistency with the angular correlation, in terms of the $\chi^2$
statistics did not help to discard any additional models with a
significant degree of confidence.

These 30 models can be classified into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

When we additional include the ACF constraint we find that only models with 
$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
are now consistent with observations.

Including all the observational constraints we find that only between $15$ to $20$ 
models reproduces observations. The list for the model parameters is in the
Appendix in Table \ref{table:models_match}.

\subsection{Observational estimates for the occupation fraction}

Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
European Southern 
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

We limit the occupation fraction to
be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
and the uncertainty in the dust correction used to infer the escape fraction. 
Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
With this additional constraint between $35$ to $40$ models are
consistent with observations, this represents a factor of $\sim 2$
reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
excluded and the best models are now clustered around a narrow region
in parameter space. %The list for the model parameters is in the
%Appendix in Table \ref{table:models_match}.

>>>>

where the sum is done over all the $13$ angle values $\theta_i$ where the
ACF has been computed. We found that 35 out of 100 models  has statistical significance 
greater that $10\%$ ($\chi^{2}<18$ that for 12 degrees). Therefore, 
in spite of the effect of cosmic variance and statistical we can rule out about
$70\%$ of the consistent models with the ACF observational constraint.

@@

The fitting is done to both the mean ACF and the observational
ACF reported by \cite{Hayashino2004} .  The results are shown 
in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
plane where the average and standard deviation for each mock 
are shown in comparison with the result derived from observations. 
Error bars in these figures represents the standard deviation of the

It can be seen in the left panel figure \ref{figure:correlation_parameters} that
The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
constrains on the parameters models. Only models with angular-correlation lenght within  
$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models. 
It is important to note that the compatible models that have been found by this power
approach are in accordance with the models found using the $\chi^{2}$ statistic.

@@

In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraint
in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
models with $f_{occ} > 0.2$.

Finally, in figure \ref{fig:ACF_prediction} we also present the ACF 
in the case of the full SSA22 region which has been homogeneously
observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions.  The full list ofthese correlation functions can
be found in the the data repository for this paper in \verb"github".

%In Figure X we present the results for the models. The full list of
%these correlation functions can be found in the the data repository
%for this paper in \verb"github".

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
\end{center}
\caption{Best models when both the constraints on the maximal number
  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
  0.2$ are included. \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*} 
%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
%\end{center} 
%\caption{ mean ACFs   and their correponding standard deviation (error
%  bars)  of some selected models in different mass ranges over the 7
%  subfields of the SSA22 field (left) and the entire 12 field sample
%  (rigth) using the  random
%  configuration. \label{figure:correlation_random} }   
%\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/power_law_correlation_prediction.pdf}
%\hspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/mean_correlation_prediction.pdf}
\end{center}
\caption{Predited ACF parameters (left panel) and ACF (rigth panel) in the full SSA22
field for the models that are consistent with observations \label{fig:ACF_prediction}} 
\end{figure*}

When we include the tightest constraints on the mock catalogs: : the
distribution of the number density and the  consistency with 
the angular correlation, we find
that there are 40 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$. The parameter space of these models
is constraint on $M_{\rm min}$ and $M_{\rm max}$ where
$\log_{10}M_{\rm min}\leq 11.3$ and $\log_{10}M_{\rm max}\leq 12.0$ 
are now consistent with observations.

These 40 models can be classified into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<0.5$ dex. While in the second familiy the
extent $>0.5$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.3}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In the next section we
discuss the implications of the existence of these two families of
models.

\subsection{Additional  Constraints on the Occupation Fraction}

We impose an additional restriction using the observational results
by \cite{Hayes2010}. They constrained the value of $f_{\rm
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

We limit the occupation fraction to
be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
and the uncertainty in the dust correction used to infer the escape fraction. 
Figure  \ref{fig:restriction_mock_and_f_occ_corr}  shows the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$ 
for the {\tt match} method after applying the observational constraint
in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
models with $f_{occ} > 0.2$.

 With this additional constraint between $15$ to $20$ models are
consistent with observations, this represents an aditional factor of $\sim 2$
reduction. The list for the model parameters is in the Appendix 
in Table \ref{table:models_match}.
%All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
%excluded and the best models are now clustered around a narrow region
%in parameter space.

In addition to this, we can also see in Figure \ref{fig:restriction_mock_and_f_occ_corr}
 that all the models excluded with  the occupation fraction  constraint ($f_{\rm occ}>0.2$)
 has $\log_{10}M_{\rm min}\geq 11.0$ and  belongs to the family 
where the range $M_{\rm min}-M_{\rm max}$ is narrow (typically of less than $<0.5$ dex).
Consequentely, our models predict that LAEs tend to live in a broad mass range
(typically of greater than $<0.5$ dex).

% In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
% models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rmmin}-f_{\rm occ}$
% for the {\tt match} method after applying the observational constraint
% in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
% models with $f_{occ}\gt0.2$.

Finally, in figure \ref{fig:ACF_prediction} we also present the ACF 
in the case of the full SSA22 region which has been homogeneously
observed by \citep{Yamada2012}. To
this date the observational ACF has not been reported in the
litereature, therefore our calculations can be considered as
predictions that could help us to make additional constrainst to our model
. The full list ofthese correlation functions can
be found in the the data repository for this paper in \verb"github".

%The list for the model parameters is in the
%Appendix in Table \ref{table:models_match}.

% 
% \begin{figure*}
% \begin{center}
% \includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
% \hspace{5mm}
% \includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
% \end{center} 
% \caption{Best models when both the constraints on the maximal number
%   of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
%   0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
% \end{figure*}
